\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generated pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Benjamin Duong} \\ \vspace{1pt}
    \small (858) 999-7513 $|$ 
    \href{mailto:benhduong@gmail.com}{benhduong@gmail.com} $|$ 
    \href{https://linkedin.com/in/benhduong}{linkedin.com/in/benhduong/} $|$
    \href{https://github.com/benhduong}{github.com/benhduong}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Georgia Institute of Technology}{Atlanta, GA}
      {Master of Science in Computer Science}{Expected May 2027}
    \resumeSubheading
      {Brown University}{Providence, RI}
      {Bachelor of Science in Computer Science}{Conferred May 2024}
      \resumeItemListStart
        \resumeItem{\textbf{Courses}: Blockchains \& Cryptocurrencies, Hypertext/Hypermedia, Intro to Robotics, Real-time \& Embedded Software, Data Science, Deep Learning, Machine Learning, Software Security \& Exploitation, User Interface \& User Experience, Fundamentals of Computer Systems, Computer Vision, Intro to Software Engineering, Intro to Algorithms \& Data Structures, Digital Computing Systems, Intro to Programming \& Computer Science}
        \resumeItem{\textbf{Extracurriculars}: Full Stack at Brown, Hack@Brown (2023, 2024), Brown Chess Club (USATE 2022; Inter-Ivy 2022, 2023) }
    \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Full-Stack Intern}{Oct 2023 -- May 2024}
      {Serre Lab, Brown University}{Providence, RI}
      \resumeItemListStart
        \resumeItem{Contributed to the development of ClickMe and RVIS, collecting and analyzing over 200,000 data points for psychophysics experiments to enhance AI models.}
        \resumeItem{Participated in weekly remote meetings to brainstorm ideas and provide updates on deliverables.}
        \resumeItem{Managed version control and collaborated with a team of three using Git and GitHub, ensuring seamless integration and continuous deployment.}
        \resumeItem{Authored technical documentation to support ongoing development and new developer onboarding.}
      \resumeItemListEnd

    \resumeSubheading
      {Undergraduate Teaching Assistant}{Jan 2022 -- May 2023}
      {ENGN 0500 Digital Computing Systems}{Providence, RI}
      \resumeItemListStart
        \resumeItem{Assisted a class of fifty students on digital logic design, assembly, finite state machines, and programming ARM microprocessor boards using C during weekly hours.}
    \resumeItemListEnd
    
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{ClickMe} $|$ \emph{React (Typescript), Golang, Postgres, Docker}}{Nov 2023 -- May 2024}
          \resumeItemListStart
            \resumeItem{Engineered frontend components such as a countdown clock and dynamic award badge for the leaderboard.}
            \resumeItem{Optimized new user signup by redesigning the default landing page.}
            \resumeItem{Selected key synset labels from Imagenet for improved data collection.}
          \resumeItemListEnd
          
      \resumeProjectHeading
          {\textbf{Rapid Visual Categorization} $|$ \emph{React, Node, Express, SQLite, Docker}}{Oct 2023 -- May 2024}
          \resumeItemListStart
            \resumeItem{Implemented secure password storage through encryption with salt and use of Google Recaptcha to verify users and reduce cheating.}
            \resumeItem{Developed a dashboard using React and Chakra UI for easy viewing of data and user management.}
            \resumeItem{Dockerized the website to run on Brown’s Google Cloud Linux VM.}
          \resumeItemListEnd
          
      \resumeProjectHeading
          {\textbf{Dabble} $|$ \emph{React, Python, MongoDB}}{Feb 2024}
          \resumeItemListStart
            \resumeItem{Leveraged GPT and retrieval augmented generation (RAG) techniques to create an AI assistant to help students navigate Courses at Brown.}
            \resumeItem{Created a user-friendly frontend interface using React and Chakra UI.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
    
%-----------PROGRAMMING SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, JavaScript, TypeScript, HTML, CSS, Golang, SQL} \\
     \textbf{Libraries/Frameworks}{: React, Chakra UI, Next.js, Node.js, Express} \\
     \textbf{Developer Tools}{: Git, Docker, Firebase} \\
    }}
 \end{itemize}
%-------------------------------------------

\end{document}
